Quantum parallel parallel Markov chain Monte Carlo

### 2021-11-23 main.tex
quantum min figure
more caption

@@

>>>>

 \begin{figure}[!t]
	\centering
	\includegraphics[width=0.9\linewidth]{qMinAlg.pdf}
	\caption{Total number of oracle evaluations required by quantum minimization algorithm \citep{durr1996quantum} for different starting ranks and search set sizes $N$ from 500 independent simulations each.  Less than 1\% of the 12,500 instances failed to recover the true minimum.}\label{fig:qMinAlg}
\end{figure}

@@

 \begin{figure}[!t]
	\centering
	\includegraphics[width=0.9\linewidth]{mcmcIterations.pdf}
	\caption{Total number of oracle evaluations required for each of 2,000 parallel MCMC iterations. In total, the combined MCMC runs required roughly $7$\% of the usual 20 million target evaluations. Over  99.4\% of the 10,000 MCMC iterations successfully sampled from the discrete distribution with probabilities of Equation \eqref{eq:probs}.}\label{fig:mcmcIterations}
\end{figure}
